The Ex-Ante View of Recommender System Design

### 2019-09-16 paper/filter_bubbles.tex
bleh

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[WWW '20]{Recomme '18: ACM Symposium on Neural Gaze Detection}{April 20--24, 2020}{Taipei, Taiwan}
\acmBooktitle{WWW '20: ACM Conference on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

@@

To counteract this problem, alternative recommendation evaluation metrics have been proposed such as serendipity
\cite{kotkov2016survey, kotkov2016challenges}. Ideally, serendipitous recommendations ``have the quality of being both unexpected and useful" \cite{maksai2015predicting}. \cite{iaquinta2010can} defines serendipitous recommendations as follows:
\begin{quote}
\textit{A serendipitous recommendation helps the
user to find a surprisingly interesting item that
she might not have otherwise discovered (or it
would have been really hard to discover). [...]
Serendipity cannot happen if the user already
knows what is recommended to her, because a
serendipitous happening is by definition something new. Thus the lower is the probability that user knows an item, the higher is the
probability that a specific item could result
in a serendipitous recommendation}.
\end{quote}

>>>>

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}
\acmConference[WWW '20]{Recomme '18: ACM Symposium on Neural Gaze Detection}{April 20--24, 2020}{Taipei, Taiwan}
\acmBooktitle{WWW '20: ACM Conference on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

@@

We simulate over a grid of $\gamma, \sigma, \rho, \beta$. When we consider results varying a single parameter, we group the results over the other parameters and consider the differences in value only varying the parameter of interest. We report results for a relatively small $T$. Unless otherwise reported, our results are robust to varying $N$.

@@

As a result, there is a need to define alternative recommendation evaluation metrics that result in recommender systems that are more useful for users. One recent alternative has been proposed such as serendipity
\cite{kotkov2016survey, kotkov2016challenges}. Ideally, serendipitous recommendations ``have the quality of being both unexpected and useful" \cite{maksai2015predicting}. \cite{iaquinta2010can} defines serendipitous recommendations as follows:
\begin{quote}
\textit{A serendipitous recommendation helps the
user to find a surprisingly interesting item that
she might not have otherwise discovered (or it
would have been really hard to discover). [...]
Serendipity cannot happen if the user already
knows what is recommended to her, because a
serendipitous happening is by definition something new. Thus the lower is the probability that user knows an item, the higher is the
probability that a specific item could result
in a serendipitous recommendation}.
\end{quote}
